### 2023-11-29 draft_jss/draft_jss.Rmd
add dividing by maximum

Reservoir Computing (RC) is a prominent machine learning methodology proposed by 
that has gained significant attention in recent years for its ability to
effectively process information generated by dynamical systems [@kim_health_2020, @maass_real-time_2002]. This
innovative approach leverages the dynamics of a high-dimensional
reservoir to perform complex computations and solve various tasks based
on the response of this dynamical system to input signals. RC has demonstrated its efficacy in tackling various challenges, encompassing pattern classification and time series forecasting in applications ranging from electrocardiogram analysis to bird calls, power plants, internet traffic, stock prices, and beyond [@tanaka_recent_2019].

@@

The utilization of RC poses challenges on multiple fronts. Firstly, its stochastic nature, attributed to the random aspect of the reservoir, introduces unpredictability into the results, even with well-chosen hyperparameters. Secondly, RC relies on numerous hyperparameters to establish connections between neurons. Despite this, guidance on determining these hyperparameters is limited, often requiring users to adopt a wrapper approach where combinations of hyperparameter performance are assessed on a training set before selecting the optimal combination. Thirdly, there is a current absence of implementation in R, rendering the method challenging for users unfamiliar with Python [@trouvain_reservoirpy_2020, @steiner_pyrcn_2022] or Julia [@martinuzzi_reservoircomputingjl_2022].

>>>>

Reservoir Computing (RC) is a prominent machine learning methodology, proposed by @kim_health_2020 and @maass_real-time_2002,
that has gained significant attention in recent years for its ability to
effectively process information generated by dynamical systems. This
innovative approach leverages the dynamics of a high-dimensional
reservoir to perform complex computations and solve various tasks based
on the response of this dynamical system to input signals. RC has demonstrated its efficacy in tackling various challenges, encompassing pattern classification and time series forecasting in applications ranging from electrocardiogram analysis to bird calls, power plants, internet traffic, stock prices, and beyond [@tanaka_recent_2019].

@@

The utilization of RC poses challenges on multiple fronts. Firstly, its stochastic nature, attributed to the random aspect of the reservoir, introduces unpredictability into the results, even with well-chosen hyperparameters. Secondly, RC relies on numerous hyperparameters to establish connections between neurons. Guidance on determining these hyperparameters is limited, often requiring users to adopt a wrapper approach where combinations of hyperparameter performance are assessed on a training set before selecting the optimal combination. Thirdly, there is a current absence of implementation in R, rendering the method challenging for users unfamiliar with Python [@trouvain_reservoirpy_2020, @steiner_pyrcn_2022] or Julia [@martinuzzi_reservoircomputingjl_2022].
